Brownian Dynein Model

### 2015-12-26 latex/derivation.tex
Add nm cartesian derivatives which need checking.
Add solutions for farbound case, which are symmetric. Improve bothbound figure to properly represent farbound motor angle Theta_fm. Update coefficients definitions for cartesian velocities. TODO: Solve matrix, input matrix solution into dynein_struct, input coefficients into dynein_struct.

\begin{align}
  X_{nm} &= \frac{L_s^2L^2 - L_t^2L^2 - L_s^2L_{f}^2 + L_t^2L_{f}^2}{4L_n^2L} + \frac{L + L_s^2 + L_n^2 - L_t^2 - L_{f}^2}{4L}\\
  &\mp L_s\sqrt{1-\frac{L^4 + L_f^4 - 2L^2L_f^2}{4L^2L_{n}^2} - \frac{L_n^2 + 2L^2 - 2L_f^2}{4L^2}}*\\
  &\sqrt{1-\frac{L_s^4 + L_t^4 - 2L_s^2L_t^2}{4L_{s}^2L_{n}^2} - \frac{L_n^2 + 2L_s^2 - 2L_t^2}{4L_s^2}}\\
  Y_{nm} &= \frac{L_{s}^2+L_{n}^2-L_{t}^2}{2L_{n}}\sqrt{1-\frac{L^4 + L_f^4 - 2L^2L_f^2}{4L^2L^2_{n}} - \frac{L_n^2 + 2L^2 - 2L_f^2}{4L^2}}\\
  &\pm L_s\frac{L^2+L_{n}^2-L_{f}^2}{2LL_{n}}\sqrt{1 - \frac{L_s^4 + L_t^4 - 2L_s^2L_t^2}{4L_s^2L_n^2} - \frac{L_n^2 + 2L_s^2 - 2L_f^2}{4L_s^2}}\\
\end{align}

Now i'm here. Just fixed the above, now go redo these derivations.\\
Now we derive with respect to time. Things which are time-dependent: $L_n, L_f$.
\subsection{New derivation}
\begin{align}
  hi
\end{align}

\subsection{Old derivation}
\begin{align}
  \dot{X}_{nm} &= \frac{1}{{2L_n^{-3}LL_s}}\left(-L_s^2L^2 - L_n^2L^2 + L_t^2L^2 - L_s^2L_{n}^2 - L_n^2L_{n}^2 + L_t^2L_{n}^2 + L_s^2L_{f}^2 + L_n^2L_{f}^2 - L_t^2L_{f}^2\right)\dot{L}_n\\ &+ \frac{2L_nL^2\dot{L}_n + 2L_s^2L_{n}\dot{L}_n + 4L_n^3\dot{L}_n - 2L_t^2L_{n}\dot{L}_n - 2L_s^2L_{f}\dot{L}_f - 2L_nL_{f}^2\dot{L}_n - 2L_n^2L_{f}\dot{L}_f + 2L_t^2L_{f}\dot{L}_f}{4L_n^2LL_s}\\
  &\mp L_s\frac{\frac{d}{dt}\left(1-\frac{L^4 + L_n^2L^2 - L_f^2L^2 + L^2L_{n}^2 + L_{n}^4 - L_f^2L_{n}^2 - L^2L_{f}^2 + L_n^2L_{f}^2 + L_{f}^4}{2LL_{n}}\right)}{2\sqrt{1-\frac{L^4 + L_n^2L^2 - L_f^2L^2 + L^2L_{n}^2 + L_{n}^4 - L_f^2L_{n}^2 - L^2L_{f}^2 + L_n^2L_{f}^2 + L_{f}^4}{2LL_{n}}}}*\\
  &\sqrt{1-\frac{L_{s}^4 + L_n^2L_{s}^2 - L_t^2L_{s}^2 + L_s^2L_{n}^2 + L_{n}^4 - L_t^2L_{n}^2 - L_s^2L_{t}^2 - L_n^2L_{t}^2 + L_{t}^4}{2L_{s}L_{n}}}\\
  &\mp L_s\sqrt{1-\frac{L^4 + L_n^2L^2 - L_f^2L^2 + L^2L_{n}^2 + L_{n}^4 - L_f^2L_{n}^2 - L^2L_{f}^2 + L_n^2L_{f}^2 + L_{f}^4}{2LL_{n}}}*\\
  &\frac{\frac{d}{dt}\left(1-\frac{L_{s}^4 + L_n^2L_{s}^2 - L_t^2L_{s}^2 + L_s^2L_{n}^2 + L_{n}^4 - L_t^2L_{n}^2 - L_s^2L_{t}^2 - L_n^2L_{t}^2 + L_{t}^4}{2L_{s}L_{n}}\right)}{2\sqrt{1-\frac{L_{s}^4 + L_n^2L_{s}^2 - L_t^2L_{s}^2 + L_s^2L_{n}^2 + L_{n}^4 - L_t^2L_{n}^2 - L_s^2L_{t}^2 - L_n^2L_{t}^2 + L_{t}^4}{2L_{s}L_{n}}}}\\
\end{align}

\begin{align}
  \dot{X}_{nm} &= \frac{-L_s^2L^2 - L_n^2L^2 + L_t^2L^2 - L_s^2L_{n}^2 - L_n^2L_{n}^2 + L_t^2L_{n}^2 + L_s^2L_{f}^2 + L_n^2L_{f}^2 - L_t^2L_{f}^2}{{2L_n^{3}LL_s}}\dot{L}_n\\ &+ \frac{2L_nL^2\dot{L}_n + 2L_s^2L_{n}\dot{L}_n + 4L_n^3\dot{L}_n - 2L_t^2L_{n}\dot{L}_n - 2L_s^2L_{f}\dot{L}_f - 2L_nL_{f}^2\dot{L}_n - 2L_n^2L_{f}\dot{L}_f + 2L_t^2L_{f}\dot{L}_f}{4L_n^2LL_s}\\
  &\mp L_s\frac{\left(\frac{L^4 + L_n^2L^2 - L_f^2L^2 + L^2L_{n}^2 + L_{n}^4 - L_f^2L_{n}^2 - L^2L_{f}^2 + L_n^2L_{f}^2 + L_{f}^4}{2LL^2_{n}} - \frac{2L_nL^2\dot{L}_n - 2L_fL^2\dot{L}_f + 2L^2L_{n}\dot{L}_n + 4L_{n}^3\dot{L}_n - 2L^2L_{f}\dot{L}_f  + 4L_{f}^3\dot{L}_f}{2LL_{n}}\right)}{2\sqrt{1-\frac{L^4 + L_n^2L^2 - L_f^2L^2 + L^2L_{n}^2 + L_{n}^4 - L_f^2L_{n}^2 - L^2L_{f}^2 + L_n^2L_{f}^2 + L_{f}^4}{2LL_{n}}}}*\\
  &\sqrt{1-\frac{L_{s}^4 + L_n^2L_{s}^2 - L_t^2L_{s}^2 + L_s^2L_{n}^2 + L_{n}^4 - L_t^2L_{n}^2 - L_s^2L_{t}^2 - L_n^2L_{t}^2 + L_{t}^4}{2L_{s}L_{n}}}\\
  &\mp L_s\sqrt{1-\frac{L^4 + L_n^2L^2 - L_f^2L^2 + L^2L_{n}^2 + L_{n}^4 - L_f^2L_{n}^2 - L^2L_{f}^2 + L_n^2L_{f}^2 + L_{f}^4}{2LL_{n}}}*\\
  &\frac{\left(\frac{L_{s}^4 + L_n^2L_{s}^2 - L_t^2L_{s}^2 + L_s^2L_{n}^2 + L_{n}^4 - L_t^2L_{n}^2 - L_s^2L_{t}^2 - L_n^2L_{t}^2 + L_{t}^4}{2L_{s}L^2_{n}}\dot{L}_n
    - \frac{2L_nL_{s}^2\dot{L}_n + 2L_s^2L_{n}\dot{L}_n + 4L_{n}^3\dot{L}_n - 2L_t^2L_{n}\dot{L}_n - 2L_nL_{t}^2\dot{L}_n}{2L_{s}L_{n}}\right)}{2\sqrt{1-\frac{L_{s}^4 + L_n^2L_{s}^2 - L_t^2L_{s}^2 + L_s^2L_{n}^2 + L_{n}^4 - L_t^2L_{n}^2 - L_s^2L_{t}^2 - L_n^2L_{t}^2 + L_{t}^4}{2L_{s}L_{n}}}}\\
\end{align}

\begin{align}
  \dot{X}_{nm} &= \frac{-L_s^2L^2 - L_n^2L^2 + L_t^2L^2 - L_s^2L_{n}^2 - L_n^2L_{n}^2 + L_t^2L_{n}^2 + L_s^2L_{f}^2 + L_n^2L_{f}^2 - L_t^2L_{f}^2}{{2L_n^{3}LL_s}}\dot{L}_n\\
  &+ \frac{2L_nL^2 + 2L_s^2L_{n} + 4L_n^3 - 2L_t^2L_{n} - 2L_nL_{f}^2\dot{L}_n}{4L_n^2LL_s}\dot{L}_n + \frac{-2L_s^2L_{f} - 2L_n^2L_{f} + 2L_t^2L_{f}}{4L_n^2LL_s}\dot{L}_f\\
  &\mp L_s\frac{\left(\frac{L^4 + L_n^2L^2 - L_f^2L^2 + L^2L_{n}^2 + L_{n}^4 - L_f^2L_{n}^2 - L^2L_{f}^2 + L_n^2L_{f}^2 + L_{f}^4}{2LL^2_{n}} - \frac{2L_nL^2 + 2L^2L_{n} + 4L_{n}^3}{2LL_{n}}\right)}{2\sqrt{1-\frac{L^4 + L_n^2L^2 - L_f^2L^2 + L^2L_{n}^2 + L_{n}^4 - L_f^2L_{n}^2 - L^2L_{f}^2 + L_n^2L_{f}^2 + L_{f}^4}{2LL_{n}}}}*\\
  &\sqrt{1-\frac{L_{s}^4 + L_n^2L_{s}^2 - L_t^2L_{s}^2 + L_s^2L_{n}^2 + L_{n}^4 - L_t^2L_{n}^2 - L_s^2L_{t}^2 - L_n^2L_{t}^2 + L_{t}^4}{2L_{s}L_{n}}}\dot{L}_n\\
  &\mp L_s\frac{\left(-\frac{-2L_fL^2 - 2L^2L_{f} + 4L_{f}^3}{2LL_{n}}\right)}{2\sqrt{1-\frac{L^4 + L_n^2L^2 - L_f^2L^2 + L^2L_{n}^2 + L_{n}^4 - L_f^2L_{n}^2 - L^2L_{f}^2 + L_n^2L_{f}^2 + L_{f}^4}{2LL_{n}}}}*\\
  &\sqrt{1-\frac{L_{s}^4 + L_n^2L_{s}^2 - L_t^2L_{s}^2 + L_s^2L_{n}^2 + L_{n}^4 - L_t^2L_{n}^2 - L_s^2L_{t}^2 - L_n^2L_{t}^2 + L_{t}^4}{2L_{s}L_{n}}}\dot{L}_f\\
  &\mp L_s\sqrt{1-\frac{L^4 + L_n^2L^2 - L_f^2L^2 + L^2L_{n}^2 + L_{n}^4 - L_f^2L_{n}^2 - L^2L_{f}^2 + L_n^2L_{f}^2 + L_{f}^4}{2LL_{n}}}*\\
  &\frac{\left(\frac{L_{s}^4 + L_n^2L_{s}^2 - L_t^2L_{s}^2 + L_s^2L_{n}^2 + L_{n}^4 - L_t^2L_{n}^2 - L_s^2L_{t}^2 - L_n^2L_{t}^2 + L_{t}^4}{2L_{s}L^2_{n}}
    - \frac{2L_nL_{s}^2 + 2L_s^2L_{n} + 4L_{n}^3 - 2L_t^2L_{n} - 2L_nL_{t}^2}{2L_{s}L_{n}}\right)}{2\sqrt{1-\frac{L_{s}^4 + L_n^2L_{s}^2 - L_t^2L_{s}^2 + L_s^2L_{n}^2 + L_{n}^4 - L_t^2L_{n}^2 - L_s^2L_{t}^2 - L_n^2L_{t}^2 + L_{t}^4}{2L_{s}L_{n}}}}\dot{L}_n\\
\end{align}

\begin{align}
  \dot{X}_{nm} &= \Bigg(\frac{-L_s^2L^2 - L_n^2L^2 + L_t^2L^2 - L_s^2L_{n}^2 - L_n^2L_{n}^2 + L_t^2L_{n}^2 + L_s^2L_{f}^2 + L_n^2L_{f}^2 - L_t^2L_{f}^2}{{2L_n^{3}L}}\\
  &+ \frac{2L_nL^2 + 2L_s^2L_{n} + 4L_n^3 - 2L_t^2L_{n} - 2L_nL_{f}^2}{4L_n^2L}\\
  &\mp \frac{\sqrt{1-\frac{L_{s}^4 + L_n^2L_{s}^2 - L_t^2L_{s}^2 + L_s^2L_{n}^2 + L_{n}^4 - L_t^2L_{n}^2 - L_s^2L_{t}^2 - L_n^2L_{t}^2 + L_{t}^4}{4L_{s}^2L_{n}^2}}}{2\sqrt{1-\frac{L^4 + L_n^2L^2 - L_f^2L^2 + L^2L_{n}^2 + L_{n}^4 - L_f^2L_{n}^2 - L^2L_{f}^2 + L_n^2L_{f}^2 + L_{f}^4}{4L^2L_{n}^2}}}*\\
  &\left(L_s\frac{L^4 + L_n^2L^2 - L_f^2L^2 + L^2L_{n}^2 + L_{n}^4 - L_f^2L_{n}^2 - L^2L_{f}^2 + L_n^2L_{f}^2 + L_{f}^4}{4L^2L^3_{n}} - L_s\frac{2L_nL^2 + 2L^2L_{n} + 4L_{n}^3}{4L^2L_{n}^2}\right)\\
  &\mp \left(L_s\frac{L_{s}^4 + L_n^2L_{s}^2 - L_t^2L_{s}^2 + L_s^2L_{n}^2 + L_{n}^4 - L_t^2L_{n}^2 - L_s^2L_{t}^2 - L_n^2L_{t}^2 + L_{t}^4}{4L_{s}^2L^3_{n}}
    - L_s\frac{2L_nL_{s}^2 + 2L_s^2L_{n} + 4L_{n}^3 - 2L_t^2L_{n} - 2L_nL_{t}^2}{4L_{s}^2L_{n}^2}\right)\\
  &\frac{\sqrt{1-\frac{L^4 + L_n^2L^2 - L_f^2L^2 + L^2L_{n}^2 + L_{n}^4 - L_f^2L_{n}^2 - L^2L_{f}^2 + L_n^2L_{f}^2 + L_{f}^4}{2LL_{n}}}}{2\sqrt{1-\frac{L_{s}^4 + L_n^2L_{s}^2 - L_t^2L_{s}^2 + L_s^2L_{n}^2 + L_{n}^4 - L_t^2L_{n}^2 - L_s^2L_{t}^2 - L_n^2L_{t}^2 + L_{t}^4}{2L_{s}L_{n}}}}\Bigg)\dot{L}_n\\
  &\Bigg(\frac{-2L_fL_s^2 - 2L_fL_n^2 + 2L_fL_t^2}{4LL_{n}^2}
  \mp L_s\frac{\sqrt{1-\left(\frac{L_s^4 + L_s^2L_n^2 - L_s^2L_t^2 L_n^2L^2 + L_n^4 - L_n^2L_f^2 - L_f^2L^2 - L_f^2L_n^2 + L_f^4}{4L_{s}^2L_{n}^2}\right)}}{2\sqrt{1 - \left(\frac{L^4 + L^2L_n^2 - L^2L_f^2 + L_n^2L^2 + L_n^4 - L_n^2L_f^2 - L_f^2L^2 - L_f^2L_n^2 + L_f^4}{4L^2L_{n}^2}\right)}}
  *\left(\frac{2L^2L_f - 2L_n^2L_f - 2L_fL^2 - 2L_fL_n^2 + 4L_f^3}{4L^2L_{n}^2}\right)\\
  &\mp L_s\frac{\sqrt{1 - \left(\frac{L^4 + L^2L_n^2 - L^2L_f^2 + L_n^2L^2 + L_n^4 - L_n^2L_f^2 - L_f^2L^2 - L_f^2L_n^2 + L_f^4}{4L^2L_{n}^2}\right)}}{2\sqrt{1-\left(\frac{L_s^4 + L_s^2L_n^2 - L_s^2L_t^2 L_n^2L^2 + L_n^4 - L_n^2L_f^2 - L_f^2L^2 - L_f^2L_n^2 + L_f^4}{4L_{s}^2L_{n}^2}\right)}}
  *\left(\frac{-2L_n^2L_f - 2L_fL^2 - 2L_fL_n^2 + 4L_f^3}{4L_{s}^2L_{n}^2}\right)\Bigg)\dot{L}_f\\
    %% &+ \Bigg(\frac{-L_s^2L_{f} - L_n^2L_{f} + L_t^2L_{f}}{2L_n^2L} \mp L_s\frac{\sqrt{1-\frac{L_{s}^4 + L_n^2L_{s}^2 - L_t^2L_{s}^2 + L_s^2L_{n}^2 + L_{n}^4 - L_t^2L_{n}^2 - L_s^2L_{t}^2 - L_n^2L_{t}^2 + L_{t}^4}{2L_{s}L_{n}}}}{2\sqrt{1-\frac{L^4 + L_n^2L^2 - L_f^2L^2 + L^2L_{n}^2 + L_{n}^4 - L_f^2L_{n}^2 - L^2L_{f}^2 + L_n^2L_{f}^2 + L_{f}^4}{2LL_{n}}}}*\\
  %% &\left(-\frac{-2L_fL^2 - 2L^2L_{f} + 4L_{f}^3}{2LL_{n}}\right)\Bigg)\dot{L}_f\\
\end{align}

We now do the same for $\dot{Y}_{nm}$.

\begin{align}
  Y_{nm} &= \frac{L_{s}^2+L_{n}^2-L_{t}^2}{2L^2_{n}} \sqrt{L_n^2-\frac{L^4 + L_n^2L^2 - L_f^2L^2 + L^2L_{n}^2 + L_{n}^4 - L_f^2L_{n}^2 - L^2L_{f}^2 - L_n^2L_{f}^2 + L_{f}^4}{4L^2}}\\
  &\pm L_s\frac{L^2+L_{n}^2-L_{f}^2}{2LL^2_{n}}\sqrt{L^2_n - \frac{L_{s}^4 + L_n^2L_{s}^2 - L_t^2L_{s}^2 + L_s^2L_{n}^2 + L_{n}^4 - L_t^2L_{n}^2 - L_s^2L_{t}^2 - L_n^2L_{t}^2 + L_{t}^4}{4L^2_{s}}}\\
\end{align}

>>>>

\begin{align}
  X_{nm} &= \frac{L_s^2L^2 - L_t^2L^2}{4L_n^2L} + \frac{-L_s^2L_{f}^2 + L_t^2L_{f}^2}{4L_n^2L} + \frac{L + L_s^2 + L_n^2 - L_t^2 - L_{f}^2}{4L}\\
  &\mp L_s\sqrt{1 - \frac{L^2}{4L_n^2} - \frac{L_f^4 - 2L^2L_f^2}{4L^2L_n^2} - \frac{L_n^2 + 2L^2 - 2L_f^2}{4L^2}}*\\
  &\sqrt{1 - \frac{L_s^4 + L_t^4 - 2L_s^2L_t^2}{4L_{s}^2L_{n}^2} - \frac{L_n^2 + 2L_s^2 - 2L_t^2}{4L_s^2}}\\  
  Y_{nm} &= \frac{L_{s}^2+L_{n}^2-L_{t}^2}{2L_{n}}\sqrt{1 - \frac{L^2}{4L_{n}^2} - \frac{L_f^4 - 2L^2L_f^2}{4L^2L^2_{n}} - \frac{L_n^2 + 2L^2 - 2L_f^2}{4L^2}}\\
  &\pm L_s\frac{L^2+L_{n}^2-L_{f}^2}{2LL_{n}}\sqrt{1 - \frac{L_s^4 + L_t^4 - 2L_s^2L_t^2}{4L_s^2L_n^2} - \frac{L_n^2 + 2L_s^2 - 2L_f^2}{4L_s^2}}\\
\end{align}

Now we derive with respect to time. Things which are time-dependent: $L_n, L_f$.

\begin{align}
  \dot{X}_{nm} &= \frac{-L_s^2L^2 + L_t^2L^2}{2L_n^3L}\dot{L}_n + \frac{-L_s^2L_{f} + L_t^2L_{f}}{2L_n^2L}\dot{L}_f + \frac{L_s^2L_{f}^2 - L_t^2L_{f}^2}{2L_n^3L}\dot{L}_n\\
  &\mp L_s\frac{\sqrt{1 - \frac{L_s^4 + L_t^4 - 2L_s^2L_t^2}{4L_{s}^2L_{n}^2} - \frac{L_n^2 + 2L_s^2 - 2L_t^2}{4L_s^2}}}{2\sqrt{1 - \frac{L^2}{4L_n^2} - \frac{L_f^4 - 2L^2L_f^2}{4L^2L_n^2} - \frac{L_n^2 + 2L^2 - 2L_f^2}{4L^2}}}\left(\frac{L^2}{2L_n^3}\dot{L}_n - \frac{L_f^3 - L^2L_f}{L^2L_n^2}\dot{L}_f + \frac{L_f^4 - 2L^2L_f^2}{2L^2L_n^3}\dot{L}_n - \frac{L_n}{2L^2}\dot{L}_n + \frac{L_f}{L^2}\dot{L}_f\right)\\
  &\mp \frac{L_s\sqrt{1 - \frac{L^2}{4L_n^2} - \frac{L_f^4 - 2L^2L_f^2}{4L^2L_n^2} - \frac{L_n^2 + 2L^2 - 2L_f^2}{4L^2}}}{2\sqrt{1 - \frac{L_s^4 + L_t^4 - 2L_s^2L_t^2}{4L_{s}^2L_{n}^2} - \frac{L_n^2 + 2L_s^2 - 2L_t^2}{4L_s^2}}}
  \left(\frac{L_s^4 + L_t^4 - 2L_s^2L_t^2}{2L_{s}^2L_{n}^3}\dot{L}_n - \frac{L_n}{2L_s^2}\dot{L}_n\right)
\end{align}

\begin{align}
  \dot{Y}_{nm} &= \left(1 - \frac{L_{s}^2+L_{n}^2-L_{t}^2}{2L_n^2}\right)\sqrt{1 - \frac{L^2}{4L_{n}^2} - \frac{L_f^4 - 2L^2L_f^2}{4L^2L^2_{n}} - \frac{L_n^2 + 2L^2 - 2L_f^2}{4L^2}}\dot{L}_n\\
  &+ \frac{L_{s}^2+L_{n}^2-L_{t}^2}{4L_{n}\sqrt{1 - \frac{L^2}{4L_{n}^2} - \frac{L_f^4 - 2L^2L_f^2}{4L^2L^2_{n}} - \frac{L_n^2 + 2L^2 - 2L_f^2}{4L^2}}}\left(\frac{L^2}{2L_n^3}\dot{L}_n - \frac{L_f^3 - L^2L_f}{L^2L^2_{n}}\dot{L}_f + \frac{L_f^4 - 2L^2L_f^2}{2L^2L^3_n}\dot{L}_n - \frac{L_n}{2L^2}\dot{L}_n + \frac{L_f}{L^2}\dot{L}_f\right)\\
  &\pm L_s\left(\frac{1}{L}\dot{L}_n - \frac{L_f}{LL_{n}}\dot{L}_f - \frac{L^2+L_{n}^2-L_{f}^2}{2LL_n^2}\dot{L}_n\right)\sqrt{1 - \frac{L_s^4 + L_t^4 - 2L_s^2L_t^2}{4L_s^2L_n^2} - \frac{L_n^2 + 2L_s^2 - 2L_f^2}{4L_s^2}}\\
  &\pm L_s\frac{L^2+L_{n}^2-L_{f}^2}{4LL_{n}\sqrt{1 - \frac{L_s^4 + L_t^4 - 2L_s^2L_t^2}{4L_s^2L_n^2} - \frac{L_n^2 + 2L_s^2 - 2L_f^2}{4L_s^2}}}\left(\frac{L_s^4 + L_t^4 - 2L_s^2L_t^2}{2L_s^2L_n^3}\dot{L}_n - \frac{L_n}{2L_s^2}\dot{L}_n + \frac{L_f}{L_s^2}\dot{L}_f\right)
\end{align}

\begin{align}
  \dot{X}_{nm} &= \Bigg[\frac{-L_s^2L^2 + L_t^2L^2}{2L_n^3L} + \frac{-L_s^2L_{f} + L_t^2L_{f}}{2L_n^2L} + \frac{L_s^2L_{f}^2 - L_t^2L_{f}^2}{2L_n^3L}\\
  &\mp L_s\frac{\sqrt{1 - \frac{L_s^4 + L_t^4 - 2L_s^2L_t^2}{4L_{s}^2L_{n}^2} - \frac{L_n^2 + 2L_s^2 - 2L_t^2}{4L_s^2}}}{2\sqrt{1 - \frac{L^2}{4L_n^2} - \frac{L_f^4 - 2L^2L_f^2}{4L^2L_n^2} - \frac{L_n^2 + 2L^2 - 2L_f^2}{4L^2}}}\left(\frac{L^2}{2L_n^3} + \frac{L_f^4 - 2L^2L_f^2}{2L^2L_n^3} - \frac{L_n}{2L^2}\right)\\
  &\mp \frac{L_s\sqrt{1 - \frac{L^2}{4L_n^2} - \frac{L_f^4 - 2L^2L_f^2}{4L^2L_n^2} - \frac{L_n^2 + 2L^2 - 2L_f^2}{4L^2}}}{2\sqrt{1 - \frac{L_s^4 + L_t^4 - 2L_s^2L_t^2}{4L_{s}^2L_{n}^2} - \frac{L_n^2 + 2L_s^2 - 2L_t^2}{4L_s^2}}}
  \left(\frac{L_s^4 + L_t^4 - 2L_s^2L_t^2}{2L_{s}^2L_{n}^3} - \frac{L_n}{2L_s^2}\right)\Bigg]\dot{L}_n\\
  &\mp \Bigg[L_s\frac{\sqrt{1 - \frac{L_s^4 + L_t^4 - 2L_s^2L_t^2}{4L_{s}^2L_{n}^2} - \frac{L_n^2 + 2L_s^2 - 2L_t^2}{4L_s^2}}}{2\sqrt{1 - \frac{L^2}{4L_n^2} - \frac{L_f^4 - 2L^2L_f^2}{4L^2L_n^2} - \frac{L_n^2 + 2L^2 - 2L_f^2}{4L^2}}}\left(-\frac{L_f^3 - L^2L_f}{L^2L_n^2} + \frac{L_f}{L^2}\right)\Bigg]\dot{L}_f\\
\end{align}

\begin{align}
  \dot{Y}_{nm} &= \bigg[\left(1 - \frac{L_{s}^2+L_{n}^2-L_{t}^2}{2L_n^2}\right)\sqrt{1 - \frac{L^2}{4L_{n}^2} - \frac{L_f^4 - 2L^2L_f^2}{4L^2L^2_{n}} - \frac{L_n^2 + 2L^2 - 2L_f^2}{4L^2}}\\
    &+ \frac{L_{s}^2+L_{n}^2-L_{t}^2}{4L_{n}\sqrt{1 - \frac{L^2}{4L_{n}^2} - \frac{L_f^4 - 2L^2L_f^2}{4L^2L^2_{n}} - \frac{L_n^2 + 2L^2 - 2L_f^2}{4L^2}}}\left(\frac{L^2}{2L_n^3} + \frac{L_f^4 - 2L^2L_f^2}{2L^2L^3_n} - \frac{L_n}{2L^2}\right)\\
    &\pm L_s\left(\frac{1}{L} - \frac{L^2+L_{n}^2-L_{f}^2}{2LL_n^2}\right)\sqrt{1 - \frac{L_s^4 + L_t^4 - 2L_s^2L_t^2}{4L_s^2L_n^2} - \frac{L_n^2 + 2L_s^2 - 2L_f^2}{4L_s^2}}\\
    &\pm L_s\frac{L^2+L_{n}^2-L_{f}^2}{4LL_{n}\sqrt{1 - \frac{L_s^4 + L_t^4 - 2L_s^2L_t^2}{4L_s^2L_n^2} - \frac{L_n^2 + 2L_s^2 - 2L_f^2}{4L_s^2}}}\left(\frac{L_s^4 + L_t^4 - 2L_s^2L_t^2}{2L_s^2L_n^3} - \frac{L_n}{2L_s^2}\right)
  \bigg]\dot{L}_n\\
  &+\bigg[\frac{L_{s}^2+L_{n}^2-L_{t}^2}{4L_{n}\sqrt{1 - \frac{L^2}{4L_{n}^2} - \frac{L_f^4 - 2L^2L_f^2}{4L^2L^2_{n}} - \frac{L_n^2 + 2L^2 - 2L_f^2}{4L^2}}}\left(-\frac{L_f^3 - L^2L_f}{L^2L^2_{n}} + \frac{L_f}{L^2}\right)\\
    &\pm L_s\left(-\frac{L_f}{LL_{n}}\right)\sqrt{1 - \frac{L_s^4 + L_t^4 - 2L_s^2L_t^2}{4L_s^2L_n^2} - \frac{L_n^2 + 2L_s^2 - 2L_f^2}{4L_s^2}}\\
    &\pm L_s\frac{L^2+L_{n}^2-L_{f}^2}{4LL_{n}\sqrt{1 - \frac{L_s^4 + L_t^4 - 2L_s^2L_t^2}{4L_s^2L_n^2} - \frac{L_n^2 + 2L_s^2 - 2L_f^2}{4L_s^2}}}\left(\frac{L_f}{L_s^2}\right)
  \bigg]\dot{L}_f
\end{align}

\subsection{Solving for $X_{fm}$ and $Y_{fm}$}
The only way to differentiate the near- and far-bound sides of the molecule is by looking at the definition of $L_n$ and $L_f$. Because of this, to calculate the values of $X_{fm}$ and $Y_{fm}$, we can just switch all instances of $L_n$ and $L_f$.

\begin{align}
  \dot{X}_{fm} &= \Bigg[\frac{-L_s^2L^2 + L_t^2L^2}{2L_f^3L} + \frac{-L_s^2L_n + L_t^2L_n}{2L_f^2L} + \frac{L_s^2L_n^2 - L_t^2L_n^2}{2L_f^3L}\\
  &\mp L_s\frac{\sqrt{1 - \frac{L_s^4 + L_t^4 - 2L_s^2L_t^2}{4L_{s}^2L_f^2} - \frac{L_f^2 + 2L_s^2 - 2L_t^2}{4L_s^2}}}{2\sqrt{1 - \frac{L^2}{4L_f^2} - \frac{L_n^4 - 2L^2L_n^2}{4L^2L_f^2} - \frac{L_f^2 + 2L^2 - 2L_n^2}{4L^2}}}\left(\frac{L^2}{2L_f^3} + \frac{L_n^4 - 2L^2L_n^2}{2L^2L_f^3} - \frac{L_f}{2L^2}\right)\\
  &\mp \frac{L_s\sqrt{1 - \frac{L^2}{4L_f^2} - \frac{L_n^4 - 2L^2L_n^2}{4L^2L_f^2} - \frac{L_f^2 + 2L^2 - 2L_n^2}{4L^2}}}{2\sqrt{1 - \frac{L_s^4 + L_t^4 - 2L_s^2L_t^2}{4L_{s}^2L_f^2} - \frac{L_f^2 + 2L_s^2 - 2L_t^2}{4L_s^2}}}
  \left(\frac{L_s^4 + L_t^4 - 2L_s^2L_t^2}{2L_{s}^2L_f^3} - \frac{L_f}{2L_s^2}\right)\Bigg]\dot{L}_f\\
  &\mp \Bigg[L_s\frac{\sqrt{1 - \frac{L_s^4 + L_t^4 - 2L_s^2L_t^2}{4L_{s}^2L_f^2} - \frac{L_f^2 + 2L_s^2 - 2L_t^2}{4L_s^2}}}{2\sqrt{1 - \frac{L^2}{4L_f^2} - \frac{L_n^4 - 2L^2L_n^2}{4L^2L_f^2} - \frac{L_f^2 + 2L^2 - 2L_n^2}{4L^2}}}\left(-\frac{L_n^3 - L^2L_n}{L^2L_f^2} + \frac{L_n}{L^2}\right)\Bigg]\dot{L}_n\\
\end{align}

\begin{align}
  \dot{Y}_{fm} &= \bigg[\left(1 - \frac{L_{s}^2+L_f^2-L_{t}^2}{2L_f^2}\right)\sqrt{1 - \frac{L^2}{4L_f^2} - \frac{L_n^4 - 2L^2L_n^2}{4L^2L^2_{n}} - \frac{L_f^2 + 2L^2 - 2L_n^2}{4L^2}}\\
    &+ \frac{L_{s}^2+L_f^2-L_{t}^2}{4L_f\sqrt{1 - \frac{L^2}{4L_f^2} - \frac{L_n^4 - 2L^2L_n^2}{4L^2L^2_{n}} - \frac{L_f^2 + 2L^2 - 2L_n^2}{4L^2}}}\left(\frac{L^2}{2L_f^3} + \frac{L_n^4 - 2L^2L_n^2}{2L^2L_f^3} - \frac{L_f}{2L^2}\right)\\
    &\pm L_s\left(\frac{1}{L} - \frac{L^2+L_f^2-L_n^2}{2LL_f^2}\right)\sqrt{1 - \frac{L_s^4 + L_t^4 - 2L_s^2L_t^2}{4L_s^2L_f^2} - \frac{L_f^2 + 2L_s^2 - 2L_n^2}{4L_s^2}}\\
    &\pm L_s\frac{L^2+L_f^2-L_n^2}{4LL_f\sqrt{1 - \frac{L_s^4 + L_t^4 - 2L_s^2L_t^2}{4L_s^2L_f^2} - \frac{L_f^2 + 2L_s^2 - 2L_n^2}{4L_s^2}}}\left(\frac{L_s^4 + L_t^4 - 2L_s^2L_t^2}{2L_s^2L_f^3} - \frac{L_f}{2L_s^2}\right)
  \bigg]\dot{L}_f\\
  &+\bigg[\frac{L_{s}^2+L_f^2-L_{t}^2}{4L_f\sqrt{1 - \frac{L^2}{4L_f^2} - \frac{L_n^4 - 2L^2L_n^2}{4L^2L^2_{n}} - \frac{L_f^2 + 2L^2 - 2L_n^2}{4L^2}}}\left(-\frac{L_n^3 - L^2L_n}{L^2L^2_{n}} + \frac{L_n}{L^2}\right)\\
    &\pm L_s\left(-\frac{L_n}{LL_f}\right)\sqrt{1 - \frac{L_s^4 + L_t^4 - 2L_s^2L_t^2}{4L_s^2L_f^2} - \frac{L_f^2 + 2L_s^2 - 2L_n^2}{4L_s^2}}\\
    &\pm L_s\frac{L^2+L_f^2-L_n^2}{4LL_f\sqrt{1 - \frac{L_s^4 + L_t^4 - 2L_s^2L_t^2}{4L_s^2L_f^2} - \frac{L_f^2 + 2L_s^2 - 2L_n^2}{4L_s^2}}}\left(\frac{L_n}{L_s^2}\right)
  \bigg]\dot{L}_n
\end{align}
